Recommendations For Intelligent Code Reorganization

### 2016-08-24 Manuscript.tex
Validity Section Update. Figures reorganized.

	This paper describes one approach to evaluate whether code reorganizations that change the structure of code are likely to have a perceivable benefit by evaluating:
	\bi
	\item If there is no evidence in the historical record that changing ``X'' is useful;
	\item Then discourage developers from doing ``X''.
	\ei
	We use data mining to generate two oracles: a {\em primary
		change oracle} and a {\em secondary verification oracle}.
	By combining these two oracles,
	we can generate and validate useful
	changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klocwerk [REF].

@@

	\subsubsection{ Alves et al.}
	Alves et al.~\cite{Alves2010} propose another approach 
	to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
	Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights of for the system. 
	The normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
	Alves et al. then select a percentage value (they suggest 90\%) which represents the ``normal'' values for metrics. The metric threshold, then, is the metric value for which 90\% of the classes fall below. The intuition  is that the worst code has outliers beyond 90\% of the normal code measurements. Hermans et al.~\cite{hermans15} used the
	Alves et al. method in their  2015 paper on
	exploring bad smells.

	For consistency with Shatnawi, we explore the correlation between the code metrics and the defect counts and  reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).

@@

		\section{Threats to Validity}\label{sect:valid}

The results of this paper are biased by our choice of code reorganization goal (reducing defects) and our choice
of measures collected from software project (OO measures such as
  depth of inheritance, number of child classes, etc).

  That said, it should be possible extend the methods of this paper to other kinds of goals (e.g. maintainability, reliability, security,
  or the knowledge sharing measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of inputs (e.g. the process measures favored by Rahman, Devanbu et al.\cite{Rahman2013})  as follows:
  \bi
  \item Find a data source for the other measures of interest;
  \item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
\item Implement a better primary verification oracle that can do ``better'' that XTREE at finding changes (where ``better'' is defined in terms 
of the opinions of the verification oracle).
\ei
To assist other researchers exploring these points, we offer a full replication package for this study at  https://github.com/ai-se/XTREE\_IST.

The results of this paper are also specific to the data sets explored here.
Such sampling bias threatens any data mining experiment; i.e., what matters
{\em there} may not be true {\em here}. For example, the data sets used here comes from a survey of
open source JAVA projects from Jureczko et al.~\cite{jureczko10}. Any biases in their selection procedures
threaten the validity of these results.

@@

		% Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.  
		% That said, we have taken care to document in this paper the decisions made by engineering
		% judgement that could effect our conclusions.

>>>>

	This paper describes one approach to evaluate whether code reorganizations that change the structure of code are likely to have a perceivable benefit by evaluating:
	\bi
	\item If there is no evidence in the historical record that changing ``X'' is useful;
	\item Then discourage developers from doing ``X''.
	\ei
	We use data mining to generate two oracles: a {\em primary
		change oracle} and a {\em secondary verification oracle}.
	By combining these two oracles,
	we can generate and validate useful
	changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klockwork\footnote{http://www.klocwork.com/}.

@@

	\subsubsection{ Alves et al.}
	Alves et al.~\cite{Alves2010} propose another approach 
	to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
	Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights of for the system. 
	The normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
	Alves et al. then select a percentage value (they suggest 90\%) which represents the ``normal'' values for metrics. The metric threshold, then, is the metric value for which 90\% of the classes fall below. The intuition  is that the worst code has outliers beyond 90\% of the normal code measurements. Hermans et al.~\cite{hermans15} used the
	Alves et al. method in their  2015 paper on
	exploring bad smells. For consistency with Shatnawi, we explore the correlation between the code metrics and the defect counts and  reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).

@@

\section{Reliability and Validity of Conclusions}
\label{sect:valid}

The results of this paper are biased by our choice of code reorganization 
goal (reducing defects) and our choice of measures collected from software 
project (OO measures such as depth of inheritance, number of child classes, 
etc). That said, it should be possible extend the methods of this paper to other 
kinds of goals (e.g. maintainability, reliability, security, or the knowledge sharing
measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of 
inputs (e.g. the process measures favored by Rahman, 
Devanbu et al.~\cite{Rahman2013})

\subsection{Reliability}
Reliability refers to the consistency of the results obtained
from the research. It has at least two components: internal
and external reliability.

Internal reliability checks if an independent researcher
reanalyzing the data would come to the same conclusion. 
To assist other researchers exploring this point, we offer a full replication package for this study at  
https://github.com/ai-se/XTREE\_IST.

External reliability assesses how well independent researchers
could reproduce the study. To increase external
reliability, this paper has taken care to clearly define our
algorithms. Also, all the data used in this work is available
online.

For the research wishing to reproduce our work to other kinds of goals, we offer the following advice:

\bi
\item Find a data source for the other measures of interest;
\item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
\item Implement a better primary verification oracle that can do ``better'' than XTREE at finding changes (where ``better'' is defined in terms 
of the opinions of the verification oracle).
\ei

\subsection{Validity}

Validity refers to the extent to which a piece of research actually
investigates what the researcher purports to investigate.
Validity has at least three components: internal and
external validity.

\subsection{Internal Validity}
The results of this paper are also specific to the data sets explored here.
Such sampling bias threatens any data mining experiment; i.e., what matters
{\em there} may not be true {\em here}. For example, the data sets used here comes from a survey of
open source JAVA projects from Jureczko et al.~\cite{jureczko10}. Any biases in their selection procedures
threaten the validity of these results.

@@
